SHARP II: Dark Matter Substructure, Gravitational Lens flux-ratio Anomalies, and the Case of B1555+375: Beware the Effect of Edge-on Disks

### 2015-08-04 papers/B1555_EdgeOn/B1555_letter.tex
minor change in B1555 paper draft

As a first trial of modelling, we create a single SIE model to check
the performance of a simple lensing potential. Consistent with
previous studies \citep{Marlow99, Xu14}, a single elliptical
potential model cannot \textbf{reproduce} the flux anomaly in B1555+375.
\textbf{Our next step is to examine if an edge-on disk can cause similar perturbations in the stong lensing system like substructures which resulting in flux ratio anomalies within merging images. In \citet{Kee98}, they explore strong lensing by spiral glaxies with the SIE+exponential disk+NFW model, corresponding to the bulge, disk, and halo respectively. Among most of mass profiles, exponential disk profile best describes the disk component in spiral galaxies because it matches the light distribution of disk. We thus choose a SIE plus exponential disk model (SIE+expdisk) in our study of B1555+375, focusing on the role of its edge-on disk in lens modelling. }
%We then create two separate models of the lensing potential that both
%incorporate the disk.  In the first we treat the lens as a SIE bulge\textbf{/halo}
%and an exponential edge-on disk (SIE+expdisk). In the second model
%the disk is represented as a very elongated SIE component (2-SIE). 
The lens system is red, with a strong jump in flux between the F814W
(roughly I) and F160W (roughly H) bands (Fig.~\ref{fig:multiband}), so
we assign a lens redshift of $z_\ell = 1.0$ and a source redshift of
$z_s =1.5$. \textbf{This assumption on redshifts is needed because some lens model parameters contain distance information. However, our choice of redshifts does not affect the predicted magnifications nor flux-ratios.}

>>>>

As a first trial of modelling, we create a single SIE model to check
the performance of a simple lensing potential. Consistent with
previous studies \citep{Marlow99, Xu14}, a single elliptical
potential model cannot \textbf{reproduce} the flux anomaly in B1555+375.
\textbf{Our next step is to examine if an edge-on disk can cause similar perturbations in the stong lensing system like substructures which resulting in flux ratio anomalies within merging images. In \citet{Kee98}, they explore strong lensing by spiral glaxies with the SIE+exponential disk+NFW model, corresponding to the bulge, disk, and halo respectively. Among most of mass profiles, exponential disk profile best describes the disk component in spiral galaxies because it matches the light distribution of disk \citep{Kee98}. We thus choose a SIE plus exponential disk model (SIE+expdisk) in our study of B1555+375, focusing on the role of its edge-on disk in lens modelling. Detail definition of mass profiles in {\tt gravlens} 
  can be found in \citet{Kee01}.}
%We then create two separate models of the lensing potential that both
%incorporate the disk.  In the first we treat the lens as a SIE bulge\textbf{/halo}
%and an exponential edge-on disk (SIE+expdisk). In the second model
%the disk is represented as a very elongated SIE component (2-SIE). 
The lens system is red, with a strong jump in flux between the F814W
(roughly I) and F160W (roughly H) bands (Fig.~\ref{fig:multiband}), so
we assign a lens redshift of $z_\ell = 1.0$ and a source redshift of
$z_s =1.5$. \textbf{This assumption on redshifts is needed because some lens model parameters contain distance information. However, our choice of redshifts does not affect the predicted magnifications nor flux-ratios.}
